Parsing Tweets into Universal Dependencies

### 2017-08-15 paper.tex
sync.

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
	\end{dependency}
	\caption{A example tweet contains major non-syntactic tokens, with
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet mark},
		\textcolor{gray}{topical hashtag}, and
		\textcolor{blue}{referential URL}.}\label{fig:non-syn-toks}
\end{figure*}

@@

\subsection{POS Tagging}
We follow the UD V2 morphology guideline and use the Universal POS tags~\cite{PETROV12.274} to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}

>>>>

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny PROPN \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
		\end{deptext}
		\deproot{1}{root}
		\depedge[edge unit distance=1em]{1}{2}{discourse}
		\deproot{6}{root}
		\depedge[edge unit distance=1em]{6}{3}{discourse}
		\depedge[edge unit distance=1em]{3}{4}{discourse}
		\depedge[edge unit distance=1em]{3}{5}{punct}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.8em]{6}{10}{obl}
		\depedge[edge unit distance=1em]{10}{8}{case}
		\depedge[edge unit distance=1em]{10}{9}{det}
		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
		\depedge[edge unit distance=0.8em]{6}{12}{list}
	\end{dependency}
	\caption{A example tweet contains major non-syntactic tokens, with
		\textcolor{red}{sentiment emoticon},
		\textcolor{orange}{retweet mark},
		\textcolor{gray}{topical hashtag}, and
		\textcolor{blue}{referential URL}.}\label{fig:non-syn-toks}
\end{figure*}

@@

\subsection{POS Tagging}
We adopt the universal Part-of-Speech (POS) tagset \cite{PETROV12.274} to annotate the tweets.
The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates typical nouns can be tagged as verbs in some certain context.
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
